Data_visualization

### 2018-06-25 Rmd/Data_visualization.Rmd
last visualization changes

library(ggplot2)
library(colorspace)
colours <- rainbow_hcl(4, start = 30, end = 300)

#load data

@@

```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6}
#Preparing seed set plots, starting with Petunia

#There are 3 crosses were seeds were lost (2,7,9)
#load libraries
library(reshape2)
library(ggplot2)
library(dplyr)

 par(mfrow=c(1,4))

@@

p <- ggplot(pein_seed_set, aes(x = Treatment, y = Seed.production)) +   geom_boxplot()+
  labs(title="Petunia integrifolia",x="", y = "Seeds")+aes(fill=Treatment)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5))

@@

p <- ggplot(some_seed_set, aes(x = Treatment, y = Seed.production)) +   geom_boxplot()+
  labs(title="Solanum melongena",x="", y = "Seeds")+aes(fill=Treatment)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5))

@@

p <- ggplot(caan_seed_set, aes(x = Treatment, y = Seed.production)) +   geom_boxplot()+
  labs(title="Capsicum annuum",x="", y = "Seeds")+aes(fill=Treatment)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5))

@@

p <- ggplot(soly_seed_set, aes(x = Treatment, y = Seed.production)) +   geom_boxplot()+
  labs(title="Solanum lycopersicum",x="", y = "Seeds")+aes(fill=Treatment)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5))

>>>>

library(ggplot2)
library(colorspace)
library(gridExtra)

colours <- rainbow_hcl(4, start = 30, end = 300)
#load data

@@

\newpage
```{r,echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6, fig.width=8,out.width='100%'}
par(mfrow=c(2,2))
#load libraries
library(reshape2)
library(ggplot2)
#read data
pein_seed_set <- read.csv("Data/PEIN_seed_set.csv", sep=";")
pein_seed_set <- pein_seed_set[-c(42,47,49),]

mean_seed_seet <- dcast(Treatment ~ ., value.var = "Seed.production", fun.aggregate = mean, data = pein_seed_set, na.rm= TRUE)

colnames(mean_seed_seet)[2] <-"avg"

sd_seed_seet <- dcast(Treatment ~ ., value.var = "Seed.production", fun.aggregate = sd, data = pein_seed_set, na.rm= TRUE)

colnames(sd_seed_seet)[2] <-"sdev"

#Unify mean and sd with merge
mean_sd <- merge(mean_seed_seet,sd_seed_seet, by="Treatment")
#Removing RARA, species not considered because sterility 
mean_sd<- mean_sd[-c(16,17),]

merge_1 <- data.frame(mean_sd, stringsAsFactors = F)

merge_1$Treatment<- as.character(merge_1$Treatment)
pein <- c("PEIN", NA, NA)

str(merge_1)
mean_sd_1 <- rbind(merge_1,pein)

#Order from lower to higher values the average, to plot it nicely
mean_sd_ordered <- mean_sd[order(mean_sd$avg),]

mean_sd_ordered_alphabetically<- mean_sd_ordered[order(mean_sd_ordered$Treatment),]

#ploting averages with sd
x <- 1:22
plot(x, mean_sd_ordered$avg,
     ylim=range(c(mean_sd_ordered$avg-mean_sd_ordered$sdev, mean_sd_ordered$avg+mean_sd_ordered$sdev)),
     pch=19, xlab="", xaxt='n', ylab="Mean +/- SD",
     main="Petunia integrifolia")
# add arrows
arrows(x, mean_sd_ordered$avg-mean_sd_ordered$sdev, x, mean_sd_ordered$avg+mean_sd_ordered$sdev, length=0.05, angle=90, code=3)
lablist.x<-as.vector(mean_sd_ordered$Treatment)
axis(x, at=1:22, labels = FALSE)
text(x, par("usr")[3] - 0.2, labels = lablist.x, cex= 0.6, adj = 1.25,srt = 45, xpd = TRUE)

some_seed_set <- read.csv("Data/SOME_seed_set.csv", sep=";")
mean_seed_seet_some <- dcast(Treatment ~ ., value.var = "seed_set", fun.aggregate = mean, data = some_seed_set, na.rm= TRUE)
colnames(mean_seed_seet_some)[2] <-"avg"
sd_seed_seet_some <- dcast(Treatment ~ ., value.var = "seed_set", fun.aggregate = sd, data = some_seed_set, na.rm= TRUE)
colnames(sd_seed_seet_some)[2] <-"sdev"

#Unify mean and sd with merge
mean_sd_some <- merge(mean_seed_seet_some,sd_seed_seet_some, by="Treatment")
#Delete RARA rows, species not included because sterility
mean_sd_some <- mean_sd_some[-c(8,9,20),]

#Order from lower to higher values the average, to plot it nicely
mean_sd_ordered_some <- mean_sd_some[order(mean_sd_some$avg),]

x <- 1:22
plot(x, mean_sd_ordered_some$avg,
     ylim=range(c(mean_sd_ordered_some$avg-mean_sd_ordered_some$sdev, mean_sd_ordered_some$avg+mean_sd_ordered_some$sdev)),
     pch=19, xlab="", xaxt='n', ylab="Mean +/- SD",
     main="Solanum melongena")
# add arrows
arrows(x, mean_sd_ordered_some$avg-mean_sd_ordered_some$sdev, x, mean_sd_ordered_some$avg+mean_sd_ordered_some$sdev, length=0.05, angle=90, code=3)
lablist.x<-as.vector(mean_sd_ordered_some$Treatment)
axis(x, at=1:22, labels = FALSE)
text(x, par("usr")[3] - 0.2, labels = lablist.x,  cex= 0.6, adj = 1.25,srt = 45, xpd = TRUE)

caan_seed_set <- read.csv("Data/CAAN_seed_set.csv", sep=";")
mean_seed_seet_caan <- dcast(treatment ~ ., value.var = "seed_set", fun.aggregate = mean, data = caan_seed_set, na.rm= TRUE)
colnames(mean_seed_seet_caan)[2] <-"avg"
sd_seed_seet_caan <- dcast(treatment ~ ., value.var = "seed_set", fun.aggregate = sd, data = caan_seed_set, na.rm= TRUE)
colnames(sd_seed_seet_caan)[2] <-"sdev"

#Unify mean and sd with merge
mean_sd_caan <- merge(mean_seed_seet_caan,sd_seed_seet_caan, by="treatment")
#Order from lower to higher values the average, to plot it nicely
mean_sd_ordered_caan <- mean_sd_caan[order(mean_sd_caan$avg),]

x <- 1:22
plot(x, mean_sd_ordered_caan$avg,
     ylim=range(c(mean_sd_ordered_caan$avg-mean_sd_ordered_caan$sdev, mean_sd_ordered_caan$avg+mean_sd_ordered_caan$sdev)),
     pch=19, xlab="", xaxt='n', ylab="Mean +/- SD",
     main="Capsicum annuum")
# add arrows
arrows(x, mean_sd_ordered_caan$avg-mean_sd_ordered_caan$sdev, x, mean_sd_ordered_caan$avg+mean_sd_ordered_caan$sdev, length=0.05, angle=90, code=3)
lablist.x<-as.vector(mean_sd_ordered_caan$treatment)
axis(x, at=1:22, labels = FALSE)
text(x, par("usr")[3] - 0.2, labels = lablist.x,  cex= 0.6, adj = 1.25,srt = 45, xpd = TRUE)

soly_seed_set <- read.csv("Data/SOLY_seed_set.csv", sep=";")
mean_seed_seet_soly <- dcast(Treatment ~ ., value.var = "seed_set", fun.aggregate = mean, data = soly_seed_set, na.rm= TRUE)
colnames(mean_seed_seet_soly)[2] <-"avg"
sd_seed_seet_soly <- dcast(Treatment ~ ., value.var = "seed_set", fun.aggregate = sd, data = soly_seed_set, na.rm= TRUE)
colnames(sd_seed_seet_soly)[2] <-"sdev"

#Unify mean and sd with merge
mean_sd_soly <- merge(mean_seed_seet_soly,sd_seed_seet_soly, by="Treatment")
#Order from lower to higher values the average, to plot it nicely
mean_sd_ordered_soly <- mean_sd_soly[order(mean_sd_soly$avg),]

x <- 1:26
plot(x, mean_sd_ordered_soly$avg,
     ylim=range(c(mean_sd_ordered_soly$avg-mean_sd_ordered_soly$sdev, mean_sd_ordered_soly$avg+mean_sd_ordered_soly$sdev)),
     pch=19, xlab="", xaxt='n', ylab="Mean +/- SD",
     main="Solanum lycopersicum")
# add arrows
arrows(x, mean_sd_ordered_soly$avg-mean_sd_ordered_soly$sdev, x, mean_sd_ordered_soly$avg+mean_sd_ordered_soly$sdev, length=0.05, angle=90, code=3)
lablist.x<-as.vector(mean_sd_ordered_soly$Treatment)
axis(x, at=1:26, labels = FALSE)
text(x, par("usr")[3] - 0.2, labels = lablist.x, cex= 0.6, adj = 1.25,srt = 45, xpd = TRUE)

\newpage
```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3.5, fig.width=5,fig.show='asis',fig.align='center',out.width='70%'}
#Preparing seed set plots, starting with Petunia

#There are 3 crosses were seeds were lost (2,7,9)
#load libraries
library(reshape2)
library(ggplot2)
library(dplyr)
library(ggplot2)
library(grid)
library(gridExtra)
library(egg)
library(gtable)

@@

plot1 <- ggplot(pein_seed_set, aes(x = Treatment, y = Seed.production)) +   geom_boxplot()+
  labs(title="Petunia integrifolia",x="", y = "Seeds")+aes(fill=Treatment)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5))

plot1 + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

@@

plot2 <- ggplot(some_seed_set, aes(x = Treatment, y = Seed.production)) +   geom_boxplot()+
  labs(title="Solanum melongena",x="", y = "Seeds")+aes(fill=Treatment)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5))

plot2 + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

@@

plot3 <- ggplot(caan_seed_set, aes(x = Treatment, y = Seed.production)) +   geom_boxplot()+
  labs(title="Capsicum annuum",x="", y = "Seeds")+aes(fill=Treatment)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5))

plot3 + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

@@

plot4 <- ggplot(soly_seed_set, aes(x = Treatment, y = Seed.production)) +   geom_boxplot()+
  labs(title="Solanum lycopersicum",x="", y = "Seeds")+aes(fill=Treatment)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5))

plot4 + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
